Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-02-23 bw-prop.tex
get heading right
phrasing

\newcommand{\authorname}{Kathryn~D.~Huff }
\newcommand{\authoremail}{katyhuff@gmail.com}
\newcommand{\authorsite}{katyhuff.github.com}

@@

\pagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text}
% Leave Left and Right Header empty.
%\lhead{}
%\rhead{}
\lhead{\textcolor{gray}{\it \authorname}}
\rhead{\textcolor{gray}{\thepage}}
%\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

@@

Initial simulations of the MSRE have been conducted both locally on the desktop 
computer scale and on Blue Wates. These have been steady state simulations and 
have occupied up to hundreds of nodes simultaneously. Coupling between 
neutronics and thermal hydraulics ahve been established in the Moltres tool, 
though validation and verification efforts are ongoing. In the near term, these 
steady state calculations will provide the initial conditions for full core 
reactor transient simulations. Such simulations commonly occupy tens of 
thousands of CPU cores at a time and vary in completion time. The MOOSE 
framework is shown to scale very well up to 10,000 cores. Transient and 
multi-scale simulations, which require greater capability per simulation, may 
occupy up to 100,000 CPU cores at a time. Only a few of those larger 
simulations are likely to be run this year..

>>>>

\newcommand{\authorname}{Kathryn~D.~Huff }
\newcommand{\authoremail}{katyhuff@gmail.com}
\newcommand{\authorsite}{arfc.npre.illinois.edu}

@@

\pagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text}
% Leave Left and Right Header empty.
%\lhead{}
%\rhead{}
\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Dr. Alexander Lindsay}}
\rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\}}
%\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

@@

Initial simulations of the MSRE have been conducted both locally on the desktop 
computer scale and on Blue Wates. These have been steady state simulations and 
have occupied up to many hundreds of nodes simultaneously. This talk will 
describe how coupling between neutronics and thermal hydraulics ahve been 
established in the Moltres tool as well as the validation and verification 
efforts which are ongoing.

In the near term, these steady state calculations will provide the initial 
conditions for full core reactor transient simulations. Such simulations 
commonly occupy tens of thousands of CPU cores at a time and vary in completion 
time. The MOOSE framework is shown to scale very well up to 10,000 cores. 
Transient and multi-scale simulations, which require greater capability per 
simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those 
larger simulations are likely to be run this year..
